formula1

### 2020-06-10 inst/f1points.Rmd
more rewriting

We can use this observation to assess a given points system: using
Monte-Carlo techniques we can generate an order table \emph{in
silico}, using estimated driver strengths from the 2017 table, and
then compare rankings generated by estimated \citeauthor{plackett1975}
strengths with rankings generated by the points system.

# Monte Carlo assumptions

@@

Now

```{r,label=montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
```

```{r,label=montecarlosetup3}
points_real
o_real <- function(n){replicate(n,resampling(m,f2017,points=points_real))}
```

now do it:

```{r,label=montecarlorealpointsdoer,cache=TRUE}
or <- o_real(1000)
```

Now some more, top n:

```{r,label=defineotop, cache = TRUE}
o_top <- function(top,n=100){replicate(n,resampling(m,f2017,points=rep(1,top)))}
```

```{r,label=executeotop1, cache = TRUE}
ot1 <- o_top(1,n=1000)
```

```{r,label=executeotop2, cache = TRUE}
ot2 <- o_top(2,n=1000)
```

```{r,label=executeotop3, cache = TRUE}
ot3 <- o_top(3,n=1000)
```

```{r,label=executeotop4, cache = TRUE}
ot4 <- o_top(4,n=1000)
```

```{r,label=executeotop5, cache = TRUE}
ot5 <- o_top(5,n=1000)
```

now some other schemes:

```{r,label=defineotherschemes}
o_zip <- function(n=100){replicate(n,resampling(m,f2017,points=1/seq_len(top)))}
o_exp <- function(p,n=100){replicate(n,resampling(m,f2017,points=p^seq_len(top)))}
```

and

```{r,label=ozcalculator,cache=TRUE}
oz <- o_zip(1000)
```

```{r,label=oecalculator,cache=TRUE}
oe <- o_exp(0.5,1000)
```

look:

```{r}
M <- rbind(
	tabulate(or +1,nbins=12),
	tabulate(ot1+1,nbins=12),
	tabulate(ot2+1,nbins=12),
	tabulate(ot3+1,nbins=12),
	tabulate(ot4+1,nbins=12),
	tabulate(ot5+1,nbins=12),
	tabulate(oz +1,nbins=12),
	tabulate(oe +1,nbins=12)
	)
dimnames(M) <- list(system=c("real",paste("top",seq_len(5)),"oz","oe"),correct=0:11)
M
```

>>>>

We can use this observation to assess a given points system: using
random sampling techniques we can generate an order table \emph{in
silico}, using estimated driver strengths from the 2017 table.  Given
this table we can then then compare rankings generated by maximum
likelihood \citeauthor{plackett1975} strengths with rankings generated
by any particular points system; this furnishes an objective assessment of a

@@

```{r,label=montecarlosetup2, cache=TRUE,echo=FALSE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
```

```{r,label=montecarlosetup3,echo=FALSE}
o_real <- function(n){replicate(n,resampling(m,f2017,points=points_real))}
```

```{r,label=montecarlorealpointsdoer,cache=TRUE,echo=FALSE}
or <- o_real(1000)
```

```{r,label=defineotop, cache = TRUE, echo=FALSE}
o_top <- function(top,n=100){replicate(n,resampling(m,f2017,points=rep(1,top)))}
```

```{r,label=executeotop1, cache = TRUE, echo=FALSE}
ot1 <- o_top(1,n=1000)
```

```{r,label=executeotop2, cache = TRUE,echo=FALSE}
ot2 <- o_top(2,n=1000)
```

```{r,label=executeotop3, cache = TRUE,echo=FALSE}
ot3 <- o_top(3,n=1000)
```

```{r,label=executeotop4, cache = TRUE,echo=FALSE}
ot4 <- o_top(4,n=1000)
```

```{r,label=executeotop5, cache = TRUE,echo=FALSE}
ot5 <- o_top(5,n=1000)
```

```{r,label=defineotherschemes, echo=FALSE}
o_zip <- function(n=100){replicate(n,resampling(m,f2017,points=1/seq_len(top)))}
o_exp <- function(p,n=100){replicate(n,resampling(m,f2017,points=p^seq_len(top)))}
```

```{r,label=ozcalculator,cache=TRUE, echo=FALSE}
oz <- o_zip(1000)
```

```{r, label=oecalculator, cache=TRUE, echo=FALSE}
oe <- o_exp(0.5,1000)
```

```{r, label=makeManddimlabel, echo=FALSE}
M <- rbind(
	tabulate(or +1,nbins=12),
	tabulate(ot1+1,nbins=12),
	tabulate(ot2+1,nbins=12),
	tabulate(ot3+1,nbins=12),
	tabulate(ot4+1,nbins=12),
	tabulate(ot5+1,nbins=12),
	tabulate(oz +1,nbins=12),
	tabulate(oe +1,nbins=12)
	)
dimnames(M) <- list(system=c("real",paste("top",seq_len(5),sep=""),"zipf","exp"),correct=0:11)
```

```{r,showM}
M
```

```{r,showcumsumM}
M2 <- t(apply(M[,12:1],1,cumsum))[,12:1]
dimnames(M2) <- list(system=rownames(M),correct=paste(">=",colnames(M2)))
M2
matplot(t(M2[,12:1]),type='b')
```
